Machine Learning Autoencoder Applied to Communication Channels

### 2019-06-12 Rapport/Article/Article.tex
Seance 06/12/2019

Communication channel error correction is key to enable digital critical communication systems to work efficiently. Although the optimal decoder for noisy channels, the maximum a posteriori (MAP) decoder, has already a mathematically proven optimal error probability minimization; its implementation cripples system applicability, since it introduces a large delay for large code words. In this context, a deep neural network (DNN) is proposed to optimize the channel with an end-to-end autoencoder. The DNN autoencoder outperforms a MAP decoder form a given encoder in terms of delay, because of the first`s \textit{one-shot} capability once trained.

@@

\begin{algorithm}
\caption{MAP rule for BSC and linear block code.}\label{euclid}
\hspace*{\algorithmicindent} \textbf{Input:} received block $\textbf{y}^n \in \{0,1\}^n$, the code word set $\mathcal{X}$ and generator matrix $G_{k \times n}$. \\
\hspace*{\algorithmicindent} \textbf{Output:} message estimation $\hat{\textbf{u}}^k \in \{0,1\}^k$.
\begin{algorithmic}[H]
\Procedure{MAP Decoder}{$y,\mathcal{X}, G$}
\State $\textit{p} \gets \text{channel crossover probability}$
\For{i in \textit{range}($2^k$)}
\State $\text{distances}[i] \gets d_H(\textbf{y},word[i] \in \mathcal{X})$
\EndFor
\State $\hat{\textbf{x}} \gets argmin(\text{distances})$
\State $\hat{\textbf{u}} $
\Return $\hat{\textbf{u}}$
\EndProcedure
\end{algorithmic}
\end{algorithm}

>>>>

Communication channel error correction is key to enable digital critical communication systems to work efficiently. The maximum a posteriori (MAP) decoder is proven to be the mathematically optimal solution for the problem. However, its implementation cripples the system applicability. This is because the MAP rule introduces a large delay for long code words. In this context, a deep neural network (DNN) is proposed to optimize the channel with an end-to-end autoencoder. The trained DNN autoencoder has a \textit{one-shot} capability which outperforms a MAP decoder for a given encoder in terms of delay. ONE PHRASE FOR RESULTS

@@

\begin{algorithm}
\caption{MAP rule for BSC and linear block code.}\label{euclid}
\hspace*{\algorithmicindent} \textbf{Input:} received block $\textbf{y}^n \in \{0,1\}^n$, the code word set $\mathcal{X}$ and generator matrix $G_{k \times n}$. \\
\hspace*{\algorithmicindent} \textbf{Output:} message estimation $\hat{\textbf{u}}^k \in \{0,1\}^k$.
\begin{algorithmic}[H]
\Procedure{MAP Decoder}{$y,\mathcal{X}, G$}
\State $\textit{p} \gets \text{channel crossover probability}$
\For{i in \textit{range}($2^k$)}
\State $\text{distances}[i] \gets d_H(\textbf{y},word[i] \in \mathcal{X})$
\EndFor
\State $\hat{\textbf{x}} \gets argmin(\text{distances})$
\State $\hat{\textbf{u}} \gets G^{-1}\hat{\textbf{x}}$
\Return $\hat{\textbf{u}}$
\EndProcedure
\end{algorithmic}
\end{algorithm}
